
---
title: "Multiple Linear Regression"
author: "Shreyu Umapathy"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(openintro)
library(GGally)
library(broom)
```



```{r}
glimpse(evals)
```

## The distribution of the `score` variable is slightly left-skewed, with most scores concentrated near the higher end (around 4 or 5). This suggests that students tend to rate professors favorably. This might be expected if students generally have a positive experience or if there's a bias toward rating leniently.

```{r}
ggplot(evals, aes(x = age, y = score)) + 
  geom_point()

ggplot(evals, aes(x = cls_students, y = cls_perc_eval)) + 
  geom_point()
```

## The first plot explores the relationship between professor age and course evaluations, while the second shows the relation between class size and response rate.

```{r}
m_bty_gen <- lm(score ~ bty_avg + gender, data = evals)
tidy(m_bty_gen)
```

## Beauty remains a statistically significant predictor of evaluation score after accounting for gender. The coefficient for `bty_avg` did not change substantially. Male professors tend to receive slightly lower scores, holding beauty constant.

```{r}
m_bty_rank <- lm(score ~ bty_avg + rank, data = evals)
tidy(m_bty_rank)
```

## R uses dummy coding to represent categorical variables with more than two levels. For example, `ranktenure track` and `ranktenured` are compared to the baseline level `teaching`.

```{r}
m_full <- lm(score ~ rank + gender + ethnicity + language + age + cls_perc_eval +
             cls_students + cls_level + cls_profs + cls_credits + bty_avg, data = evals)
summary(m_full)
```

## The variable `ethnicity` has a high p-value, indicating it's not statistically significant in the model. Removing it improves adjusted \( R^2 \) slightly, suggesting it doesn't explain unique variance. If coefficients do not change much after removal, `ethnicity` likely isn't collinear with other predictors.

```{r}
m_final <- lm(score ~ rank + gender + language + age + cls_perc_eval + bty_avg, data = evals)
summary(m_final)
```

**Model Interpretation**: Higher beauty ratings, younger age, higher evaluation response rates, and teaching rank are associated with higher course evaluations.

**Regression Assumptions**: Residuals are approximately normal and show constant variance.

**Generalizability**: Because data were only collected from one university and the same professors across courses, results may not generalize to other institutions.

